Spin canonical divisors of log stacky curves

### 2015-06-28 stacky_write_up/spin_cring.tex
minor cite changes

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. When $g \geq 2$, Petri's
theorem gives generators and relations for $R(X, K_X)$ showing that
in most cases $R(X, K_X)$ is generated in degree 1 with relations
in degree 2, as shown in \cite[p. 157]{saint-donat:proj}. This has the
pleasant geometric consequence that all such canonically embedded
curves are scheme theoretically cut out by quadratic equations.

Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many
directions. 
If $X$ is a curve, then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
$$\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
As is done in \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points. A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx,\Delta,L)$ is
\begin{align*}
	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

@@

\begin{proof}[Proof of Lemma ~\ref{lem:generation_5}]
If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
Lemma ~\ref{lem:genus-2-generation-5}. Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$. By \cite{vzb:stacky}[Theorem 3.2.1], we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6. Hence, $R_L$ is generated in degree at most 5.
\end{proof}

>>>>

\noindent
with multiplication structure corresponding to tensor product of
sections. In the case that $g \geq 2$, $\Omega_X$ is ample, so $X \cong \proj R$. When $g \geq 2$, Petri's
theorem gives generators and relations for $R(X, K_X)$ showing that
in most cases $R(X, K_X)$ is generated in degree 1 with relations
in degree 2, as shown in Saint-Donat\cite[p. 157]{saint-donat:proj}. This has the
pleasant geometric consequence that all such canonically embedded
curves are scheme theoretically cut out by quadratic equations.

Following Voight and Zureick-Brown \cite{vzb:stacky}, we generalize Petri's theorem in many
directions. 
If $X$ is a curve, then we say $\sx$ is a {\bf stacky curve} with {\bf coarse space} $X$ and {\bf stacky points} $P_1,\ldots, P_r$ with {\bf stabilizer orders} $e_1,\ldots, e_r \in \BZ_{\geq 2}$ if 
$$\di \sx = \di X \oplus \left(\bigoplus_{i
= 1}^r \left\langle \frac{1}{e_i}P_i \right\rangle \right) \subset \BQ \otimes \di X.$$
As is done in Voight and Zureick-Brown \cite{vzb:stacky} one may view a stacky curve as a stack, but for the purposes of this paper, it suffices to view $\sx$ as a scheme whose associated divisor group allows a finite number of ``fractional points,'' i.e., stacky points. A {\bf log spin curve} is a triple $(\sx, \Delta, \halfcan)$ where $\Delta \in \di X$ is an effective divisor and $2\halfcan = K_X + \Delta + \sum_{i=1}^{r}\subhalf{e_i}P_i.$
The central object of study in this paper is the {\bf log spin
canonical ring} of $(\sx,\Delta,L)$ is
\begin{align*}
	R(\sx,\Delta,L) = \bigoplus_{d \geq 0} H^0(\sx,\sco(L)^{\otimes d})
\end{align*}

@@

\begin{proof}[Proof of Lemma ~\ref{lem:generation_5}]
If $\Delta > 0$, this holds by Lemma ~\ref{lem:semicanonical_generation}. If $g = 2$ and $\Delta = 0,$ then the claim follows from
Lemma ~\ref{lem:genus-2-generation-5}. Finally, if $g > 2$ and $\Delta = 0$, using Lemma ~\ref{lem:semicanonical_generation}, there are no minimal generators in degree $\geq 7$. By Voight and Zurieck-Brown \cite[Theorem 3.2.1]{vzb:stacky}, we obtain the map $\sym^3 H^0(2L) \rightarrow \sym^3 H^0(6L)$ is surjective and so there are also no minimal generators in degree 6. Hence, $R_L$ is generated in degree at most 5.
\end{proof}
